Parametric analysis of ambisonic audio

### 2020-07-06 Chapters/ScientificBackground.tex
minor

Spherical harmonics are continuous functions defined on the sphere surface. Due to their mathematical properties, any spherical function can be decomposed as a combination of spherical harmonics, in what is known as the \textit{Spherical Harmonics Expansion} \cite{jarrett2017theory}.

>>>>

Spherical harmonics are continuous functions defined on the sphere surface. Due to their mathematical properties, any continuously differentiable spherical function can be decomposed as a combination of spherical harmonics, in what is known as the \textit{Spherical Harmonics Expansion} \cite{jarrett2017theory}.

### 2020-07-06 manuscript.tex
minor

Thanks a lot to Chedar for his company in these final steps. And, of course, million thanks to my family and to Marta for their unconditional love and support.\\

@@

%Recent years have witnessed a rise in immersive multimedia content, as a result of the developments in Virtual and Augmented Reality, where spatial audio plays a crucial role for the creation of a realistic experience. 
%Ambisonic microphones allow the recording of sound scenes while preserving their spatial characteristics. For that reason, ambisonic has turned into the \textit{de facto} standard for immersive audio transmission. Yet, few production tools exploit all the information available in such media.   
%In the present thesis we raise the research question of obtaining meaningful information from ambisonic recordings, based on the parametric analysis of the sound field.
%In order to answer the question we have developed different state-of-the-art methods, which cover a broad range of applications within the parametric audio analysis scope. 
%Specifically, we present novel contributions in the scope of blind reverberation time estimation, diffuseness estimation, and sound event localization and detection. Furthermore, several software tools developed for dataset generation and storage are also presented.

@@

%Els micròfons ambisonics permeten gravar escenes sonores preservant les seues característiques espacials. A causa d'això, ambisonics s'ha convertit en l'estàndard de facto per a la transmissió d'àudio immersiu. No obstant això, encara son poques les eines de producció que permeten explotar tota la informació disponible en aquest mitjà.
%En la present tesi plantegem la pregunta de com obtenir informació rellevant de gravacions ambisonics de manera automàtica, basant-nos en l'an\`alisi param\`etric del camp ac\'ustic. 
%%d'una forma que siga significativa per als productors.
%Per a això, hem desenvolupat una sèrie de mètodes i eines a nivell de l'estat de l'art, 
%que cobreixen un ampli espectre d'aplicaciones a l'\`ambit de l'an\`alisi param\`etric del so. 
%%que s'apliquen a diferents nivells de la cadena de producció de so immersiu; cadascun d'aquests elements representa una contribució nova a l'estat de l'art en aquest camp.
%
%%En los últimos años hemos asistido al auge del contenido multimedia immersivo, auspiciado por los avances en Realidad Virtual y Aumentada. En este medio, el sonido espacial juega un papel muy importante para la creación de una sensación de realismo.
%%
%%Los micrófonos ambisonics permiten grabar escenas sonoras preservando sus características espaciales.
%%Debido a esto, ambisonics se ha convertido en el estándar de facto para la transmisión de audio immersivo. Sin embargo, todavía hay pocas herramientas de producción que permitan explotar toda la información disponible en este medio.
%%
%%En esta tesis planteamos la pregunta de cómo obtener información relevante de grabaciones ambisonics de manera automática, de una forma significativa para los productores.
%%
%%Para ello, hemos desarrollado una serie de métodos y herramientas que se aplican a diferentes niveles de la cadena de producción de sonido immersivo; cada uno de estos elementos representa una contribución novedosa al estado del arte en ese campo.

@@

%PREFACE. 
%{\bf Preface }
\section*{\Large \sffamily  Preface}

@@

%\begin{appendices}
%\appendixpage
%\noappendicestocpagenum
%\addappheadtotoc

%\chapter{List of Contributions}
%
%In the following list we show the main scientific contributions, as main author, related to this dissertation:
%
%\begin{itemize}
%
%	\item Peer-reviewed journal articles
%	
%	\textbf{"Analysis of spherical isotropic noise fields with an A-Format tetrahedral microphone"}.
%	\underline{A. P\'erez-L\'opez} and N. Stefanakis.
%	\textit{The Journal of the Acoustical Society of America 146.4 (2019): EL329-EL334.}
%
%	\item Peer-reviewed conference articles
%
%	\textbf{"Blind reverberation time estimation from ambisonic recordings"}.
%	\underline{A. P\'erez-L\'opez}, A. Politis and E. G\'omez.
%	Submitted to \textit{IEEE 22nd International Workshop on Multimedia Signal Processing, 2020.}\\
%
%	\textbf{"PAPAFIL: a low complexity sound event localization and detection method with parametric particle filtering and gradient boosting".}
%	\underline{A. P\'erez-L\'opez} and R. Ibañez-Usach.
%	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\
%	
%	\textbf{"A hybrid parametric-deep learning approach for sound event localization and detection".}
%	\underline{A. P\'erez-L\'opez}, E. Fonseca and X. Serra.
%	In \textit{Proceedings of the Detection and Classification of Acoustic Scenes and Events 2019 Workshop (DCASE2019)}.
%	
%	\textbf{"Ambiscaper: A tool for automatic generation and annotation of reverberant ambisonics sound scenes".}\\
%	\underline{A. P\'erez-L\'opez}.
%	In \textit{Proceedings of the 16th International Workshop on Acoustic Signal Enhancement (IWAENC). IEEE, 2018.}
%	
%	
%	\item Conference engineering briefs
%
%
%	\textbf{"Ambisonics directional room impulse response as a new convention of the spatially oriented format for acoustics".}
%	\underline{A. P\'erez-L\'opez} and J. De Muynke.
%	In \textit{Proceedings of the 144th Audio Engineering Society Convention. Audio Engineering Society, 2018.}\\
%	
%	\textbf{"pysofaconventions, a Python API for SOFA".}
%	\underline{A. P\'erez-L\'opez}.
%	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\
%	
%	\textbf{"A Python library for multichannel acoustic signal processing".}
%	\underline{A. P\'erez-L\'opez} and A. Politis.
%	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\
%	
%\end{itemize}
%
%\newpage
%
%Moreover, although not strictly aligned with the research direction of this thesis, the author has supervised the following publication:\\
%
%	 \textbf{"Sound event localization and detection based on CRNN using dense rectangular filters and channel rotation data augmentation".}
%	F. Ronchini, D. Arteaga and \underline{A. P\'erez-L\'opez}.
%	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\
%
%
%
%\chapter{List of Software Resources}
%
%
%As a result of the development of this thesis, the following open-source libraries and repositories have been produced. All of them are freely available through the author's GitHub page \cite{andresgithub} under open-source licenses. 
%
%
%\begin{itemize}
%
%	\item Software tools:
%
%	\begin{itemize}
%	
%		\item \href{https://github.com/andresperezlopez/masp}{masp: Multichannel Acoustic Signal Processing library} 
%		Tools for acoustic simulation and spherical array processing. 
%		 
%		
%		\item \href{https://github.com/andresperezlopez/pysofaconventions}{pysofaconventions} Implementation of the SOFA convention in Python. 
%	
%		\item \href{https://github.com/andresperezlopez/AmbisonicsDRIR}{AmbisonicsDRIR}	 Ambisonic SOFA Convention proposal.
%
%		\item \href{https://github.com/andresperezlopez/ambiscaper}{AmbiScaper} Tool for automatic generation of annotated ambisonic datasets.
%
%	\end{itemize}
%	\newpage
%	\item Method implementations: 
%
%	\begin{itemize}
%		\item \href{https://github.com/andresperezlopez/ambisonic_rt_estimation}{ambisonic\_rt\_estimation} Contains the code implementing the methods described in Chapter~\ref{chap:rt60}.
%	
%		\item \href{https://github.com/andresperezlopez/DCASE2020}{DCASE2020} Full code implementing the SELD algorithm from Chapter~\ref{chap:seld2019}.
%	
%		\item \href{https://github.com/andresperezlopez/DCASE2019_task3}{DCASE2019\_task3} 
%		Implementation of the method submitted to DCASE2019 (not included in this thesis). 
%
%	\end{itemize}
%
%\end{itemize}
%

%\end{appendices}

>>>>

Thanks a lot to Chedar for his company in the final steps. And, of course, million thanks to my family and to Marta for their unconditional love and support, powering all the way up here. \\

@@

@@

@@

%PREFACE. 
\section*{\Large \sffamily  Preface}

@@
